Future Directions

### 2021-03-04 manuscripts/laplacian_smoothing/arXiv/minimax_optimal_laplacian_smoothing.tex
pg 1-6

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

@@

\begin{center} {\Large{\bf{Minimax Optimal Regression over Sobolev Spaces via Laplacian Regularization on Neighborhood Graphs}}}

@@

\section{INTRODUCTION}

We adopt the standard setup in nonparametric regression, where we observe samples $(X_1,Y_1),\ldots,(X_n,Y_n)$ that are i.i.d.\ draws from the model 
\begin{equation}
\label{eqn:signal_plus_noise_model}
Y_i = f_0(X_i) + \varepsilon_i, \quad \epsilon_i \sim N(0,1), 
\end{equation}
where $\varepsilon_i$ is independent of $X_i$. Our goal is to perform statistical inference on the unknown regression function $f_0$, by which we mean either \emph{estimating} $f_0$ or more simply \emph{testing} whether $f_0 = 0$, i.e., whether there is any signal present.

Laplacian smoothing \citep{smola2003} is a penalized least squares estimator, defined over a graph. Letting $G = (V,W)$ be a weighted undirected graph with vertices $V=\{1,\ldots,n\}$, associated with $\{X_1,\ldots,X_n\}$, the Laplacian smoothing estimator \smash{$\wh{f}$} is given by
\begin{equation}
\label{eqn:laplacian_smoothing}
\wh{f} =  \argmin_{f \in \Reals^n} \; \sum_{i = 1}^{n}(Y_i - f_i)^2 + \rho \cdot f^\top \Lap f. 
\end{equation}
Here $\Lap$ is the graph Laplacian matrix (to be defined in Section~\ref{sec:problem_setup_and_background}), $G$ is typically a geometric graph (such as a $k$-nearest-neighbor or neighborhood graph), $\rho \geq 0$ is a tuning parameter, and the penalty
\begin{equation*}
f^\top \Lap f = \frac{1}{2} \sum_{i,j = 1}^{n} W_{ij}(f_i - f_j)^2
\end{equation*}
encourages \smash{$\wh{f}_i \approx \wh{f}_j$} when $X_i \approx X_j$. Assuming \eqref{eqn:laplacian_smoothing} is a reasonable estimator of $f_0$, the statistic
\begin{equation}
\label{eqn:laplacian_smoothing_test}
\wh{T} = \frac{1}{n} \| \wh{f} \|_2^2 
\end{equation}
would in turn be a reasonable way to test $f_0 = 0$.

@@

For these reasons, a body of work has emerged that analyzes the statistical properties of Laplacian smoothing, and graph-based methods more generally. Roughly speaking, this work can be divided into two categories, based on the perspective they adopt. 
\begin{itemize}
	\item \emph{Fixed design perspective.} Here one treats the design points $X_1,\ldots,X_n$ and the graph $G$ as fixed, and carries out inference on $f_0(X_i)$, $i=1,\ldots,n$. In this problem setting, tight upper bounds have been derived on the error of various graph-based methods (e.g., \citet{wang2016,hutter2016,sadhanala16,sadhanala17,kirichenko2017,kirichenko2018}) and tests (e.g., \citet{sharpnack2010identifying,sharpnack2013b,sharpnack2013,sharpnack2015}), which certify that such procedures are \emph{optimal} over ``function'' classes (in quotes because these classes really model the $n$-dimensional vector of evaluations). The upside of this work is its generality: in this setting $G$ need not be a geometric graph, but in principle it could be any graph over $V=\{1,\ldots,n\}$. The downside is that, in the context of nonparametric regression, it is not as natural to think of the evaluations of $f_0$ as exhibiting smoothness over some fixed pre-defined graph $G$, and more natural to speak of the smoothness of the function $f_0$ itself. 
	\item \emph{Random design perspective.} Here one treats the design points $X_1,\ldots,X_n$ as independent samples from some distribution $P$ supported on a domain $\Xset \subseteq \Rd$. Inference is drawn on the regression function $f_0: \Xset \to \Reals$, which is typically assumed to be smooth in some \emph{continuum} sense, e.g., it possesses a first derivative bounded in $L^{\infty}$ (H\"{o}lder) or $\Leb^2$ (Sobolev) norm. To conduct graph-based inference, the user first builds a neighborhood graph over the random design points---so that $W_{ij}$ is large when $X_i$ and $X_j$ are close in (say) Euclidean distance---and then computes e.g., \eqref{eqn:laplacian_smoothing} or \eqref{eqn:laplacian_smoothing_test}. In this context, various graph-based procedures have been shown to be \emph{consistent}: as $n \to \infty$, they converge to a continuum limit (see \citet{belkin07,vonluxburg2008,trillos2018} among others). However, until recently such statements were not accompanied by error rates, and even so, such error rates as have been proved \citep{lee2016,trillos2020} are not optimal over continuum function spaces, such as H\"{o}lder or Sobolev classes. 
\end{itemize}
The random design perspective bears a more natural connection with nonparametric regression (the focus in this paper), as it allows us to formulate smoothness based on $f_0$ itself (how it behaves as a continuum function, and not just its evaluations at the design points). In this paper, we will adopt the random design perspective, and seek to answer the following question:
\begin{quote}{When we assume the regression function $f_0$ to be smooth in a continuum sense, does Laplacian smoothing achieve optimal performance for estimation and goodness-of-fit testing?} 
\end{quote}
This is no small question---arguably, it is \emph{the} central question of nonparametric regression---and without an answer one cannot fully compare the statistical properties of Laplacian smoothing to alternative methods. It also seems difficult to answer: as we discuss next, there is a fundamental gap between the \emph{discrete} smoothness imposed by the penalty $f^\top \Lap f$ in problem \eqref{eqn:laplacian_smoothing} and the \emph{continuum} smoothness assumed on $f_0$, and in order to obtain sharp upper bounds we will need to bridge this gap in a suitable sense.

\section{SUMMARY OF RESULTS}

@@

In light of this last point, it is worth asking whether there is any \emph{statistical} advantage to solving a discrete problem such as \eqref{eqn:laplacian_smoothing} (setting aside computational considerations for the moment). After all, we could have instead solved the following variational problem:
\begin{equation}
\label{eqn:thin_plate_spline}
\wt{f} = \argmin_{f : \Xset \to \Reals} \; \sum_{i = 1}^{n} \bigl(Y_i - f(X_i)\bigr)^2 + \rho \hspace{-2pt} \int_{\Xset} \|\nabla f(x)\|_2^2 \,dx,
\end{equation}
where the optimization is performed over all functions for which the criterion is well-defined and finite (continuous functions $f$ that have a weak derivative $\nabla f$ in $L^2(\Xset)$). Analogously, for testing, we could use:
\begin{equation}
\label{eqn:thin_plate_spline_test}
\wt{T} = \| \wt{f} \|_n^2 = \frac{1}{n} \sum_{i=1}^n \wt{f}(X_i)^2.
\end{equation}
The penalty term in \eqref{eqn:thin_plate_spline} leverages the assumption that $f_0$ has a smooth derivative in a seemingly natural way. Indeed, the estimator \smash{$\wt{f}$} and statistic \smash{$\wt{T}$} are well-known: for $d = 1$, \smash{$\wt{f}$} is the familiar \emph{smoothing spline}, and for $d>1$, it is type of a \emph{thin-plate spline}. The statistical properties of smoothing and thin-plate splines are well-understood \citep{vandergeer2000,liu2019}. As we discuss later, the Laplacian smoothing problem \eqref{eqn:laplacian_smoothing} can be viewed as a discrete and noisy approximation to \eqref{eqn:thin_plate_spline}. At first blush, this suggests that Laplacian smoothing should at best inherit the statistical properties of \eqref{eqn:thin_plate_spline}, and at worst may have meaningfully larger error.

@@

For an integer $p \geq 1$, we use $\Leb^p(\Xset)$ for the set of functions $f$ such that 
\begin{equation*}
\norm{f}_{\Leb^p(\Xset)}^p := \int_{\Xset} |f(x)|^p \,dx < \infty,
\end{equation*}
and $C^p(\Xset)$ for the set of functions that are $p$ times continuously differentiable. For sequences $a_n,b_n$, we write $a_n \lesssim b_n$ to mean $a_n \leq Cb_n$ for a constant $C>0$ and large enough $n$, and $a_n \asymp b_n$ to mean $a_n \lesssim b_n$ and $b_n \lesssim a_n$. Lastly, we use $a \wedge b = \max\{a,b\}$.

\section{BACKGROUND}
\label{sec:problem_setup_and_background}

@@

In the graph-based approach to nonparametric regression, we first build a neighborhood graph \smash{$G_{n,r} = (V,W)$}, for $V=\{1,\ldots,n\}$, to capture the geometry of $P$ (the design distribution) and $\Xset$ (the domain) in a suitable sense. The $n \times n$ weight matrix $W = (W_{ij})$ encodes proximity between pairs of design points; for a kernel function $K: [0,\infty) \to \Reals$ and radius $r > 0$, we have
\begin{equation*}
\label{eqn:neighborhood_graph}
W_{ij} = K\Biggl(\frac{\|X_i - X_j\|_2}{r}\Biggr),
\end{equation*}
with $\|\cdot\|_2$ denoting the $\ell_2$ norm on $\Rd$. Defining $D$ as the $n \times n$ diagonal matrix with entries \smash{$D_{ii} = \sum_{j = 1}^{n} W_{ij}$}, the graph Laplacian can then be written as
\begin{equation}
\label{eqn:graph_Laplacian}
\Lap_{n,r} = D - W.
\end{equation}
We add subscripts $n,r$ to $\Lap$ and $G$ to emphasize that they depend on the design points $X_1,\ldots,X_n$ and the radius $r$. To avoid any confusion: henceforth when we speak of \smash{$\wh{f}$} and \smash{$\wh{T}$}, we will always assume that they are fit using the neighborhood graph Laplacian \smash{$L = L_{n,r}$}. Writing its eigendecomposition as \smash{$L = \sum_{k = 1}^{n} \lambda_k v_k v_k^\top$}, we always assume, by convention, ordered eigenvalues $0 = \lambda_1 \leq \cdots \leq \lambda_n$, and unit-norm eigenvectors. %we will make reference to these objects later on.

@@

Under conditions~\ref{asmp:domain}, \ref{asmp:density}, the minimax estimation rate over a Sobolev ball of radius $M \geq n^{-1/2}$ is (e.g., \citet{tsybakov2008_book}):
\begin{equation}
\label{eqn:sobolev_space_estimation_minimax_rate}
\inf_{\wh{f}} \sup_{f_0 \in H^1(\Xset, M)} \Ebb\Bigl[\norm{\wh{f} - f_0}_{L^2(\Xset)}^2\Bigr] \asymp M^{2d/(2 + d)} n^{-2/(2 + d)}.
\end{equation}
% RJT: This is a bit of a weird reference, because (as per my understanding) Tsybakov only proves the rate is tight for Holder classes, which are contained in the Sobolev class. So technically from Tsybakov alone we only know \gtrsim, not \asymp for this one. It's fine, I wouldn't change anything because it would involve explaining a lot more, I'm just pointing this out.
(Throughout we assume $M \geq n^{-1/2}$, as otherwise the minimax rate is just the parametric rate $n^{-1}$.)

As nonparametric hypothesis testing is (comparatively) less familiar than nonparametric estimation, we briefly summarize the main idea before stating the optimal error rate. In the goodness-of-fit testing problem, we ask for a test function---formally, a Borel measurable function $\phi$ taking values in $\{0,1\}$---which can distinguish between the hypotheses
\begin{equation}
\mathbf{H}_0: f_0 = f_0^{\star}, ~~\textrm{versus}~~ \mathbf{H}_a: f_0 \in \mc{F} \setminus \{f_0^{\star}\}.
\end{equation} 
Typically, the null hypothesis $f_0 = f_0^{\star} \in \mc{F}$ reflects the absence of interesting structure, and $\mc{F} \setminus  \{f_0^{\star}\}$ is a set of smooth departures from this null. In this paper, as in \citet{ingster2009}, we focus on the problem of \emph{signal detection} in Sobolev spaces, where $f_0^{\star} = 0$ and $\mc{F} = H^1(\Xset,M)$ is a first-order Sobolev ball.

The minimax critical radius is the smallest value of $\epsilon$ such that some level-${\alpha}$ test $\phi$ has power at least $1 - \alpha$ over all $\mc{F}_{\epsilon} := \mc{F} \cap \{f: \|f\|_{\Leb^2(\Xset)} \geq \epsilon\}$:
\begin{equation*}
\epsilon(\mc{F}) := \inf\biggl\{\epsilon > 0: \inf_{\phi} \sup_{f_0 \in \mc{F}_{\epsilon}} \Ebb_{f_0}[1 - \phi] \leq \alpha \biggr\},
\end{equation*} 
where in the above the infimum is over all level-$\alpha$ tests $\phi$, and $\Ebb_{f_0}[\cdot]$ is the expectation operator under the regression function $f_0$.\footnote{Of course, the minimax critical radius $\epsilon$ depends on $\alpha$. However, we adopt the typical convention of treating $\alpha$ as a small but fixed positive constant; hence it will not affect the testing error rates, and we suppress it notationally.} See \citet{ingster82,ingster87,ingster2012} for a more extended treatment of the minimax paradigm in nonparametric testing.

@@

\section{MINIMAX OPTIMALITY OF LAPLACIAN SMOOTHING}
\label{sec:minimax_optimal_laplacian_smoothing}

@@

\section{MANIFOLD ADAPTIVITY}
\label{sec:manifold_adaptivity}

@@

\section{DISCUSSION}
\label{sec:discussion}

@@

\bibliographystyle{plainnat}
\bibliography{../../../graph_regression_bibliography} 
\clearpage

>>>>

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\green}[1]{\textcolor{green}{#1}}
\newcommand{\sbcomment}[1]{{\bf{{\red{{SB --- #1}}}}}}

\usepackage{natbib}
\renewcommand{\bibname}{References}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

@@

\begin{center} {\Large{\bf{Minimax Optimal Regression over Sobolev Spaces \\
\vspace{.2cm}
 via Laplacian Regularization on Neighborhood Graphs}}}

@@

\section{Introduction}

We adopt the standard nonparametric regression setup, where we observe samples $(X_1,Y_1),\ldots,(X_n,Y_n)$ that are i.i.d.\ draws from the model 
\begin{equation}
\label{eqn:signal_plus_noise_model}
Y_i = f_0(X_i) + \varepsilon_i, \quad \epsilon_i \sim N(0,1), 
\end{equation}
where $\varepsilon_i$ is independent of $X_i$. Our goal is to perform statistical inference on the unknown regression function $f_0$, by which we mean either \emph{estimating} $f_0$ or \emph{testing} whether $f_0 = 0$, i.e., whether there is any signal present.

Laplacian smoothing \citep{smola2003} is a penalized least squares estimator, defined over a graph. Letting $G = (V,W)$ be a weighted undirected graph with vertices $V=\{1,\ldots,n\}$, associated with $\{X_1,\ldots,X_n\}$, and $W \in \mathbb{R}^{n \times n}$ is the (weighted) adjacency matrix of the graph. 
the Laplacian smoothing estimator \smash{$\wh{f}$} is given by
\begin{equation}
\label{eqn:laplacian_smoothing}
\wh{f} =  \argmin_{f \in \Reals^n} \; \sum_{i = 1}^{n}(Y_i - f_i)^2 + \rho \cdot f^\top \Lap f. 
\end{equation}
Here $\Lap$ is the graph Laplacian matrix (defined formally in Section~\ref{sec:problem_setup_and_background}), $G$ is typically a geometric graph (such as a $k$-nearest-neighbor or neighborhood graph), $\rho \geq 0$ is a tuning parameter, and the penalty
\begin{equation*}
f^\top \Lap f = \frac{1}{2} \sum_{i,j = 1}^{n} W_{ij}(f_i - f_j)^2
\end{equation*}
encourages \smash{$\wh{f}_i \approx \wh{f}_j$} when $X_i \approx X_j$. Assuming \eqref{eqn:laplacian_smoothing} is a reasonable estimator of $f_0$, the statistic
\begin{equation}
\label{eqn:laplacian_smoothing_test}
\wh{T} = \frac{1}{n} \| \wh{f} \|_2^2 
\end{equation}
is in turn a natural test statistic to test if $f_0 = 0$.

@@

For these reasons, a body of work has emerged that analyzes the statistical properties of Laplacian smoothing, and graph-based methods more generally. Roughly speaking, this work can be divided into two categories, based on the perspective they adopt. 
\begin{itemize}
	\item \emph{Fixed design perspective.} Here one treats the design points $X_1,\ldots,X_n$ and the graph $G$ as fixed, and carries out inference on $f_0(X_i)$, $i=1,\ldots,n$. In this problem setting, tight upper bounds have been derived on the error of various graph-based methods (e.g., \citet{wang2016,hutter2016,sadhanala16,sadhanala17,kirichenko2017,kirichenko2018}) and tests (e.g., \citet{sharpnack2010identifying,sharpnack2013b,sharpnack2013,sharpnack2015}), which certify that such procedures are \emph{optimal} over ``function'' classes (in quotes because these classes really model the $n$-dimensional vector of evaluations). The upside of this work is its generality: in this setting $G$ need not be a geometric graph, but in principle it could be any graph over $V=\{1,\ldots,n\}$. The downside is that, in the context of nonparametric regression, it is arguably not as natural to think of the evaluations of $f_0$ as exhibiting smoothness over some fixed pre-defined graph $G$, and more natural to speak of the smoothness of the function $f_0$ itself. 
	\item \emph{Random design perspective.} Here one treats the design points $X_1,\ldots,X_n$ as independent samples from some distribution $P$ supported on a domain $\Xset \subseteq \Rd$. Inference is drawn on the regression function $f_0: \Xset \to \Reals$, which is typically assumed to be smooth in some \emph{continuum} sense, e.g., it possesses a first derivative bounded in $L^{\infty}$ (H\"{o}lder) or $\Leb^2$ (Sobolev) norm. To conduct graph-based inference, the user first builds a neighborhood graph over the random design points---so that $W_{ij}$ is large when $X_i$ and $X_j$ are close in (say) Euclidean distance---and then computes e.g., \eqref{eqn:laplacian_smoothing} or \eqref{eqn:laplacian_smoothing_test}. In this context, various graph-based procedures have been shown to be \emph{consistent}: as $n \to \infty$, they converge to a continuum limit (see \citet{belkin07,vonluxburg2008,trillos2018} among others). However, until recently such statements were not accompanied by error rates, and even so, such error rates as have been proved \citep{lee2016,trillos2020} are not optimal over continuum function spaces, such as H\"{o}lder or Sobolev classes. 
\end{itemize}
The random design perspective bears a more natural connection with nonparametric regression (the focus in this paper), as it allows us to formulate smoothness based on $f_0$ itself (how it behaves as a continuum function, and not just its evaluations at the design points). In this paper, we will adopt the random design perspective, and seek to answer the following question:
\begin{quote}{When we assume the regression function $f_0$ is smooth in a continuum sense, does Laplacian smoothing achieve optimal performance for estimation and goodness-of-fit testing?} 
\end{quote}
This is no small question---arguably, it is \emph{the} central question of nonparametric regression---and without an answer one cannot fully compare the statistical properties of Laplacian smoothing to alternative methods. It also seems difficult to answer: as we discuss next, there is a fundamental gap between the \emph{discrete} smoothness imposed by the penalty $f^\top \Lap f$ in problem \eqref{eqn:laplacian_smoothing} and the \emph{continuum} smoothness assumed on $f_0$, and in order to obtain sharp upper bounds we will need to bridge this gap in a suitable sense.

\section{Summary of Results}

@@

In light of the potential difficulty in bridging the gap between discrete and continuum notions of smoothness, it is worth asking whether there is any \emph{statistical} advantage to solving a discrete problem such as \eqref{eqn:laplacian_smoothing} (setting aside computational considerations for the moment). After all, we could have instead solved the following variational problem:
\begin{equation}
\label{eqn:thin_plate_spline}
\wt{f} = \argmin_{f : \Xset \to \Reals} \; \sum_{i = 1}^{n} \bigl(Y_i - f(X_i)\bigr)^2 + \rho \hspace{-2pt} \int_{\Xset} \|\nabla f(x)\|_2^2 \,dx,
\end{equation}
where the optimization is performed over all functions for which the criterion is well-defined and finite (continuous functions $f$ that have a weak derivative $\nabla f$ in $L^2(\Xset)$). Analogously, for testing, we could use:
\begin{equation}
\label{eqn:thin_plate_spline_test}
\wt{T} = \| \wt{f} \|_n^2 := \frac{1}{n} \sum_{i=1}^n \wt{f}(X_i)^2.
\end{equation}
The penalty term in \eqref{eqn:thin_plate_spline} leverages the assumption that $f_0$ has a smooth derivative in a seemingly natural way. Indeed, the estimator \smash{$\wt{f}$} and statistic \smash{$\wt{T}$} are well-known: for $d = 1$, \smash{$\wt{f}$} is the familiar \emph{smoothing spline}, and for $d>1$, it is a type of \emph{thin-plate spline}. The statistical properties of smoothing and thin-plate splines are well-understood \citep{vandergeer2000,liu2019}. As we discuss later, the Laplacian smoothing problem \eqref{eqn:laplacian_smoothing} can be viewed as a discrete and noisy approximation to \eqref{eqn:thin_plate_spline}. At first blush, this suggests that Laplacian smoothing should at best inherit the statistical properties of \eqref{eqn:thin_plate_spline}, and at worst may have meaningfully larger error.

@@

For an integer $p \geq 1$, we use $\Leb^p(\Xset)$ for the set of functions $f$ such that 
\begin{equation*}
\norm{f}_{\Leb^p(\Xset)}^p := \int_{\Xset} |f(x)|^p \,dx < \infty,
\end{equation*}
and $C^p(\Xset)$ for the set of functions that are $p$ times continuously differentiable. For sequences $a_n,b_n$, we write $a_n \lesssim b_n$ to mean $a_n \leq Cb_n$ for a constant $C>0$ and large enough $n$, and $a_n \asymp b_n$ to mean $a_n \lesssim b_n$ and $b_n \lesssim a_n$. Lastly, we use $a \wedge b = \max\{a,b\}$. \sbcomment{This is wrong, should check where it appears.}

\section{Background}
\label{sec:problem_setup_and_background}

@@

In the graph-based approach to nonparametric regression, we first build a neighborhood graph \smash{$G_{n,r} = (V,W)$}, for $V=\{1,\ldots,n\}$, to capture the geometry of $P$ (the design distribution) and $\Xset$ (the domain) in a suitable sense. The $n \times n$ weight matrix $W = (W_{ij})$ encodes proximity between pairs of design points; for a kernel function $K: [0,\infty) \to \Reals$ and radius $r > 0$, we have
\begin{equation*}
\label{eqn:neighborhood_graph}
W_{ij} = K\Biggl(\frac{\|X_i - X_j\|_2}{r}\Biggr),
\end{equation*}
with $\|\cdot\|_2$ denoting the $\ell_2$ norm on $\Rd$. Defining $D$ as the $n \times n$ diagonal matrix with entries \smash{$D_{ii} = \sum_{j = 1}^{n} W_{ij}$}, the graph Laplacian can then be written as
\begin{equation}
\label{eqn:graph_Laplacian}
\Lap_{n,r} = D - W.
\end{equation}
We add subscripts $n,r$ to $\Lap$ and $G$ to emphasize that they depend on the design points $X_1,\ldots,X_n$ and the radius $r$. To avoid any confusion: henceforth when we speak of \smash{$\wh{f}$} and \smash{$\wh{T}$}, we will always assume that they are fit using the neighborhood graph Laplacian \smash{$L = L_{n,r}$}. Writing its eigendecomposition as \smash{$L = \sum_{k = 1}^{n} \lambda_k v_k v_k^\top$}, we always assume, by convention, ordered eigenvalues $0 = \lambda_1 \leq \cdots \leq \lambda_n$, and unit-norm eigenvectors. %we will make reference to these objects later on. 
\sbcomment{Don't understand why you're switching between $L$ and $L_{n,r}$?}

@@

Under conditions~\ref{asmp:domain}, \ref{asmp:density}, the minimax estimation rate over a Sobolev ball of radius $M \geq n^{-1/2}$ is (e.g., \citet{tsybakov2008_book}):
\begin{equation}
\label{eqn:sobolev_space_estimation_minimax_rate}
\inf_{\wh{f}} \sup_{f_0 \in H^1(\Xset, M)} \Ebb\Bigl[\norm{\wh{f} - f_0}_{L^2(\Xset)}^2\Bigr] \asymp M^{2d/(2 + d)} n^{-2/(2 + d)}.
\end{equation}
% RJT: This is a bit of a weird reference, because (as per my understanding) Tsybakov only proves the rate is tight for Holder classes, which are contained in the Sobolev class. So technically from Tsybakov alone we only know \gtrsim, not \asymp for this one. It's fine, I wouldn't change anything because it would involve explaining a lot more, I'm just pointing this out.
(Throughout we assume $M \geq n^{-1/2}$, as otherwise the minimax rate is just the parametric rate $n^{-1}$.) \sbcomment{I don't think the second part of this comment is correct the way you've defined the Sobolev class.}

As minimax rates in nonparametric hypothesis testing are (comparatively) less familiar than those in nonparametric estimation, we briefly summarize the main idea before stating the optimal error rate. In the goodness-of-fit testing problem, we ask for a test function---formally, a Borel measurable function $\phi$ taking values in $\{0,1\}$---which can distinguish between the hypotheses
\begin{equation}
\mathbf{H}_0: f_0 = f_0^{\star}, ~~\textrm{versus}~~ \mathbf{H}_a: f_0 \in \mc{F} \setminus \{f_0^{\star}\}.
\end{equation} 
Typically, the null hypothesis $f_0 = f_0^{\star} \in \mc{F}$ reflects the absence of interesting structure, and $\mc{F} \setminus  \{f_0^{\star}\}$ is a set of smooth departures from this null. In this paper, as in \citet{ingster2009}, we focus on the problem of \emph{signal detection} in Sobolev spaces, where $f_0^{\star} = 0$ and $\mc{F} = H^1(\Xset,M)$ is a first-order Sobolev ball. \sbcomment{Why isn't this without loss of generality?}

\sbcomment{Define a level-$\alpha$ test.} The minimax critical radius is the smallest value of $\epsilon$ such that some level-${\alpha}$ test $\phi$ has power at least $1 - \alpha$ over all $\mc{F}_{\epsilon} := \mc{F} \cap \{f: \|f\|_{\Leb^2(\Xset)} \geq \epsilon\}$:
\begin{equation*}
\epsilon(\mc{F}) := \inf\biggl\{\epsilon > 0: \inf_{\phi} \sup_{f_0 \in \mc{F}_{\epsilon}} \Ebb_{f_0}[1 - \phi] \leq \alpha \biggr\},
\end{equation*} 
where in the above the infimum is over all level-$\alpha$ tests $\phi$, and $\Ebb_{f_0}[\cdot]$ is the expectation operator under the regression function $f_0$.\footnote{Of course, the minimax critical radius $\epsilon$ depends on $\alpha$. However, we adopt the typical convention of treating $\alpha$ as a small but fixed positive constant; hence it will not affect the testing error rates, and we suppress it notationally.} See \citet{ingster82,ingster87,ingster2012} for a more extended treatment of the minimax paradigm in nonparametric testing.

@@

\section{Minimax Optimality of Laplacian Smoothing}
\label{sec:minimax_optimal_laplacian_smoothing}

@@

\section{Manifold Adaptivity}
\label{sec:manifold_adaptivity}

@@

\section{Discussion}
\label{sec:discussion}

@@

\bibliographystyle{plainnat}
\bibliography{../../../graph_regression_bibliography}
